---
title: Building a Threadripper...for cheap!
date: 2019-02-27
author: Justin M. Shea
institute:  
titlegraphic: ~/R/University-of-Chicago-MScA-Markdown-workshop/images/UofC-logo.png
fontsize: 10pt
output:
 ioslides_presentation:
    smaller: true
    #logo: ~/R/University-of-Chicago-MScA-Markdown-workshop/images/UofC-logo.png
    css: ~/R/University-of-Chicago-MScA-Markdown-workshop/slides/ioslides-css.css    
 beamer_presentation:
    template: ~/R/University-of-Chicago-MScA-Markdown-workshop/slides/latex-beamer.tex
    keep_tex: true
# toc: true
    slide_level: 2
---


# Introduction



## About me: Justin M. Shea

- Lead organizer of [The Chicago R User Group](https://www.meetup.com/Chicago-R-User-Group/)

- Committee member [R/Finance 2019](https://www.rinfinance.com/)

- Author of the **`wooldridge`** R package, the official R package for "Introductory Econometrics" by Jeffrey M. Wooldridge.

- Author of the **`neverhpfilter`** R package, implementing James Hamilton's alternative to the Hodrick-Prescott filter.

- Visiting Professor of Finance Roosevelt University

- TA/Co-instructor UChicago Master of Science in analytics

- A long Career in Futures and Options trading

- Recent consulting for high frequency, mutual fund startup, and fund-of-funds firms.

- [Google summer of code](https://summerofcode.withgoogle.com/) mentor 2019, R and Finance applications?


# Motivations

## Motherboard and CPU

 	
AMD - Threadripper 1950X **3.4 GHz 16-Core** Processor **SALE $450**

 	
ASRock - X399 Taichi ATX TR4 Motherboard: **SALE $150**

```{r,  echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0189.JPG")
knitr::include_graphics(path)
```

## Cooling

 	
Enermax - Liqtech TR4 II 280 80.71 CFM Liquid CPU Cooler **$150**

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0190.JPG")
knitr::include_graphics(path)
```


## RAM

Corsair - Dominator Platinum 16 GB (2 x 8 GB) x 2 DDR4-3000 Memory

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0191.JPG")
knitr::include_graphics(path)
```


## RAM Installed: 64GB

Also,

G.Skill - Trident Z RGB 32 GB (4 x 8 GB) DDR4-3200 Memory

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0193.JPG")
knitr::include_graphics(path)
```

## RAM

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0194.JPG")
knitr::include_graphics(path)
```

## Corsair RAM

```{r, echo = FALSE, out.width = "600px"}
path <- paste0(getwd(), "/images/IMG_0235.JPG")
knitr::include_graphics(path)
```

## G.Skill RAM

```{r, echo = FALSE, out.width = "600px"}
path <- paste0(getwd(), "/images/IMG_0237.JPG")
knitr::include_graphics(path)
```


## Fan Cable Management

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0196.JPG")
knitr::include_graphics(path)
```

## Graphics Processing Unit (GPU)

**2GB Nvidia Gigabyte: SALE $75**

GeForce GTX 1050 2 GB Windforce OC Video Card


```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0197.JPG")
knitr::include_graphics(path)
```

## M.2 Memory is Awesome

970 Evo 250 GB M.2-2280 Solid State Drive

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0198.JPG")
knitr::include_graphics(path)
```


## Hard Drive

 	
Seagate - IronWolf 8 TB 3.5" 7200RPM Internal Hard Drive 

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0238.JPG")
knitr::include_graphics(path)
```

## Complete

```{r, echo = FALSE, out.width = "450px"}
path <- paste0(getwd(), "/images/IMG_0201.PNG")
knitr::include_graphics(path)
```

## Its Alive!!

```{r, echo = FALSE, out.width = "450px"}
path <- paste0(getwd(), "/images/IMG_0203.PNG")
knitr::include_graphics(path)
```

## Complete List of parts $1500!

But I had some parts already.

PC Part picker link: https://pcpartpicker.com/list/Xqs9zY

```{r, echo = FALSE, out.width = "750px"}
path <- paste0(getwd(), "/images/pcPartPicker.PNG")
knitr::include_graphics(path)
```

## ...actually closer to $2500

PC Part picker link: https://pcpartpicker.com/list/Xqs9zY

```{r, echo = FALSE, out.width = "750px"}
path <- paste0(getwd(), "/images/pxRecent.PNG")
knitr::include_graphics(path)
```

# Thank You!

