---
title: Building a Threadripper...for cheap!
date: 2019-02-27
author: Justin M. Shea
institute:  
titlegraphic: ~/R/University-of-Chicago-MScA-Markdown-workshop/images/UofC-logo.png
fontsize: 10pt
output:
 ioslides_presentation:
    smaller: true
    #logo: ~/R/University-of-Chicago-MScA-Markdown-workshop/images/UofC-logo.png
    css: ~/R/University-of-Chicago-MScA-Markdown-workshop/slides/ioslides-css.css    
 beamer_presentation:
    template: ~/R/University-of-Chicago-MScA-Markdown-workshop/slides/latex-beamer.tex
    keep_tex: true
# toc: true
    slide_level: 2
---


# Introduction



## About me: Justin M. Shea

- Visiting Professor of Finance Roosevelt University

- TA/Co-instructor U Chicago Master of Science in analytics

- Organizer of [The Chicago R User Group](https://www.meetup.com/Chicago-R-User-Group/)

- Committee member [R/Finance 2019](https://www.rinfinance.com/)

- Author of the **`wooldridge`** R package, the official R package for "Introductory Econometrics" by Jeffrey M. Wooldridge.

- Author of the **`neverhpfilter`** R package, implementing James Hamilton's alternative to the Hodrick-Prescott filter.

- [Google summer of code](https://summerofcode.withgoogle.com/) mentor 2019, R and Finance applications?


# Motivations

## Data grows, hardware gets cheaper

- Data Scientists: A Designer laptop that costs $3,000+ is a waste of your most valuable resources, **time & money**.

- Data Scientists: You're already building your own Software for Data Analysis (`SoDa`) for several good reason, consider building your hardware for many of these same reasons.

- Management: Experienced, Full-Stack Data Pros often command salaries in the six figures. Don't issue them the 8GB laptop, their productivity is simply too valuable to impose this bottleneck. 

- Some data is private/valuable and you may not be allowed to risk it in the cloud.


# The Build

## Motherboard and CPU

AMD - Threadripper 1950X **3.4 GHz 16-Core** Processor **Black Friday SALE $450**

ASRock - X399 Taichi ATX TR4 Motherboard: **Microcenter bargain table SALE $150**

```{r,  echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0189.JPG")
knitr::include_graphics(path)
```

## Cooling

 	
Enermax - Liqtech TR4 II 280 80.71 CFM Liquid CPU Cooler **Retail $140ish**

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0190.JPG")
knitr::include_graphics(path)
```


## Corsair RAM

Corsair - Dominator Platinum 32 GB (2 x 2 x 8 GB) DDR4-3000 Memory **Retail $320**

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0191.JPG")
knitr::include_graphics(path)
```

## Corsair RAM

These are **Samsung B-Die** sticks, higher quality for Threadrippers.

```{r, echo = FALSE, out.width = "600px"}
path <- paste0(getwd(), "/images/IMG_0235.JPG")
knitr::include_graphics(path)
```

## G.Skill RAM

Added another 32GB kit a friend had laying aroud, even if lower quality **Hynix**

- G.Skill-Trident Z RGB 32 GB (4 x 8 GB) DDR4-3200 Memory **$0**

```{r, echo = FALSE, out.width = "600px"}
path <- paste0(getwd(), "/images/IMG_0237.JPG")
knitr::include_graphics(path)
```

## RAM Installed: 64GB!

One _shouldn't_ mix differing RAM. I did because its **more RAM**!

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0193.JPG")
knitr::include_graphics(path)
```

## RAM Installed: 64GB!

If mixing `RAM`, consult the Motherboard manual for optimal slot placement.

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0194.JPG")
knitr::include_graphics(path)
```


## RAM Installed: 64GB!

When mixing `RAM`, enter the `bios` on boot and adjust the frequency higher one level at a time, until boot failure resets the frequency to default (2133 MHZ in my case). One step below boot failure is your stock maximum.

Although I'm mixing **`3000`** and **`3200`** kits, the most I was able to reach was **`2800`** MHZ without increasing memory voltage. I'll tune that another day...

```{r, echo = FALSE, out.width = "700px"}
path <- paste0(getwd(), "/images/IMG_0259.JPG")
knitr::include_graphics(path)
```

## Fan Cable Management

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0196.JPG")
knitr::include_graphics(path)
```

## Graphics Processing Unit(s)

I rely on the MSI unit for graphics, but picked up the Gigabyte unit (`pictured`) to experiment with GPU computation. At `2GB DDR5 RAM`, it has `640 CUDA cores`.

- MSI GeForce GT 710 2GB DDR3, 192 CUDA cores **Retail $50ish**

- Gigabyte GeForce GTX 1050, Windforce OC Video Card **MC Bargin Table $75**

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0197.JPG")
knitr::include_graphics(path)
```

## NVMe M.2 Memory is Awesome

Read/write data 6-7 times faster than SATA SSD!

- 970 Evo 250 GB M.2-2280 Solid State Drive **Retail Sale $88**

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0198.JPG")
knitr::include_graphics(path)
```

## 8TB Hard Drive

Seagate - IronWolf 8TB 3.5" 7200rpm Hard Drive **Retail $233**

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0238.JPG")
knitr::include_graphics(path)
```

## Its Alive!!

```{r, echo = FALSE, out.width = "450px"}
path <- paste0(getwd(), "/images/IMG_0203.PNG")
knitr::include_graphics(path)
```

## Complete List of parts $1500!

Full Disclosure: I owned parts already and am an extreme bargain hunter!

NOTE: The ENERMAX liquid cooler isn't suppose to fit the mid-tower. I made it work.

PC Part picker link for this build here: https://pcpartpicker.com/list/Xqs9zY


```{r, echo = FALSE, out.width = "750px"}
path <- paste0(getwd(), "/images/pcPartPicker.PNG")
knitr::include_graphics(path)
```

## Closer to $2500 from scratch

This route does requires your valuable time to research and build. I'd argue this initial time investment pays dividends via future upgrades, builds, and productivity.

Still cheaper than the average silver designer laptop, and more powerful!

PC Part picker link: https://pcpartpicker.com/list/Xqs9zY

```{r, echo = FALSE, out.width = "750px"}
path <- paste0(getwd(), "/images/pxRecent.PNG")
knitr::include_graphics(path)
```

# Thank You!

