---
title: Building a Threadripper for cheap
date: 2019-02-27
author: Justin M. Shea
institute:  
titlegraphic: ~/R/University-of-Chicago-MScA-Markdown-workshop/images/UofC-logo.png
fontsize: 10pt
output:
 ioslides_presentation:
    smaller: true
    #logo: ~/R/University-of-Chicago-MScA-Markdown-workshop/images/UofC-logo.png
    css: ~/R/University-of-Chicago-MScA-Markdown-workshop/slides/ioslides-css.css    
 beamer_presentation:
    template: ~/R/University-of-Chicago-MScA-Markdown-workshop/slides/latex-beamer.tex
    keep_tex: true
# toc: true
    slide_level: 2
---


# Introduction



## About me: Justin M. Shea

- Lead organizer of [The Chicago R User Group](https://www.meetup.com/Chicago-R-User-Group/)

- Committee member [R/Finance 2019](https://www.rinfinance.com/)

- Mentor for [The Johns Hopkins Data Science specialization](https://www.coursera.org/specializations/jhu-data-science) online

- Author of the **`wooldridge`** R package, the official R package for "Introductory Econometrics" by Jeffrey M. Wooldridge.

- Author of the **`neverhpfilter`** R package, implementing James Hamilton's alternative to the Hodrick-Prescott filter.

- Visiting Professor fo Finance Roosevelt University

- TA/Co-instructor U Chicago Master of Science in analytics

- A long Career in Futures and Options trading

- Recent consulting for high frequency, mutual fund, and fund of funds firms.

- [Google summer of code](https://summerofcode.withgoogle.com/) mentor 2019, R and Finance applications.


# Motivations

## Motherboard and CPU

```{r,  echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0189.JPG")
knitr::include_graphics(path)
```

## Cooling

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0190.JPG")
knitr::include_graphics(path)
```


## RAM

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0191.JPG")
knitr::include_graphics(path)
```

## RAM

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0192.JPG")
knitr::include_graphics(path)
```

## RAM

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0193.JPG")
knitr::include_graphics(path)
```

## RAM

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0194.JPG")
knitr::include_graphics(path)
```

## RAM and fans

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0196.JPG")
knitr::include_graphics(path)
```

## Graphics Processing Unit (GPU)


```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0197.JPG")
knitr::include_graphics(path)
```

## M.2 Memory 250 GB

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_0198.JPG")
knitr::include_graphics(path)
```


## Hard Drive

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_238.JPG")
knitr::include_graphics(path)
```

## It's Alive!

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/IMG_213.JPG")
knitr::include_graphics(path)
```


## Complete List of parts $1500

PC Part picker:

https://pcpartpicker.com/list/Xqs9zY

```{r, echo = FALSE, out.width = "550px"}
path <- paste0(getwd(), "/images/pcPartPicker.PNG")
knitr::include_graphics(path)
```



